---
title: "nike"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
nike<-read.csv(paste("activity.csv"),sep=",")
```

##Histogram
```{r}
steps<-aggregate(steps~date,nike,sum,na.rm=TRUE)
hist(steps$steps,breaks=20)
```

```{r}
steps<-aggregate(steps~date,nike,sum,na.rm=TRUE)
mean<-mean(steps$steps)
median<-median(steps$steps)
mean
median
```

##Time Series Plot 
```{r}
step<-aggregate(steps~interval,nike,FUN="mean",na.rm=TRUE)
avgday<-aggregate(steps~date,nike,FUN="mean",na.rm=TRUE)

plot(steps~interval,step,type="l")

maxs<-step[which.max(step$steps),]$interval

```
The `r maxs` th interval has the max average steps

###Imputing missing values in the main data

```{r}
s<-sum(is.na(nike$steps))
s
newnike<-nike
avgdays<-function(interval){
    avgday[step$interval==interval,]$steps
}
```
Thus, there are `r s`NA entries in the original data.
We can replace the NA value with the mean number of steps for that 5min time interval .


```{r}
c=0

for(i in 1:nrow(newnike))
{
  if(is.na(newnike[i,]$steps))
  {
newnike[i,]$steps<-avgdays(newnike[i,]$interval)
    c=c+1
  }
}
c
```

###Histogram of new Data
```{r}

newsteps<-aggregate(steps~date,newnike,sum)
hist(newsteps$steps)
nmean<-mean(newsteps$steps)
nmed<-median(newsteps$steps)
```
The new data mean is `r nmean`  
The new data median is `r nmed`

##Creating the weekday/ weekend column in the datasheet

```{r}
newnike$day=ifelse(as.POSIXlt(as.Date(newnike$date))$wday%%6==0,"weekend","weekday")
```

###Are there differences in activity patterns between weekdays and weekends?

```{r}
stepsInterval2=aggregate(steps~interval+day,newnike,FUN="mean")
library(lattice)
xyplot(steps~interval|factor(day),data=newnike,type="l")
```
